\documentclass[journal,10pt,onecolumn,draftclsnofoot,]{IEEEtran}
\usepackage{lipsum}
\usepackage{graphicx} 
\usepackage{microtype}
\usepackage{hyperref}

\author{
    Dario Loi --- 1940849 \and \\
    Elena Maria Muià --- 1938610 \and \\
    Martina Doku --- 1938629
}

\title{Project Proposal: ReConPatch}

\begin{document}
\maketitle
\section{abstract}

In this project, our primary objective is to explore and implement advanced computer
 vision techniques for \textbf{anomaly detection} within the context of industrial manufacturing. 

We seek to unlock its full potential in augmenting the 
efficiency and precision of anomaly detection tasks by also boosting its accuracy and reliability.
We are willing to demonstrate, with our own implementation, the effectiveness of CV based methods and their potential to be applied in real-world scenarios.
\section{objective}
We aim to reimplement and potentially advance the ReConPatch method 
     proposed in the paper titled \textbf{"ReConPatch: Anomaly Detection by Linear Modulation of
      Pretrained Features."} \cite{ReConPatch}
      This method addresses the challenge of anomaly detection by 
      constructing discriminative features through a linear modulation of patch features
       extracted from pre-trained models and employs contrastive representation learning to collect and distribute features in a way
       that produces a target-oriented and easily separable representation of the data.
\section{resources}
 We plan to compare our implementation with the original ReConPatch method
      to evaluate its performance and identify potential areas for improvement.
       We will use the data from \textbf{MVTec AD}\cite{MVTec AD} and \textbf{BTAD}\cite{BTAD} dataset that have been used in the original paper.\\
       Additionally, all the code and data will be stored in a GitHub repository for version control and collaboration,
       at the following link: \textbf{\url{https://github.com/dario-loi/ReConPatch-torch}}
    
    

\begin{thebibliography}{00}
\bibitem{ReConPatch}
Hyun, Jeeho \& Kim, Sangyun \& Jeon, Giyoung \& Kim, Seung \& Bae, Kyunghoon \& Kang, Byung. (2023). ReConPatch : Contrastive Patch Representation Learning for Industrial Anomaly Detection.
\bibitem{MVTec AD}
Paul Bergmann, Michael Fauser, David Sattlegger, and
Carsten Steger. Mvtec ad–a comprehensive real-world
dataset for unsupervised anomaly detection. In Proceedings
of the IEEE/CVF conference on computer vision and pattern
recognition, pages 9592–9600, 2019
\bibitem{BTAD}
Pankaj Mishra, Riccardo Verk, Daniele Fornasier, Claudio
Piciarelli, and Gian Luca Foresti. Vt-adl: A vision transformer 
network for image anomaly detection and localization. In 2021 IEEE
 30th International Symposium on Industrial Electronics (ISIE), pages 01–06. IEEE, 2021.
\end{thebibliography} 
\end{document}